\chapter{Market analysis}
This chapter means to examine the market for products of similar  character too this projects.

\section*{SOTX Smart Badminton Racquet}
SOTX have made a \textit{Smart Badminton Racquet} \citep{sotxsite}. This racket is labeled as having sensors and a microprocessor built into the handle and can then communicate with and Android or iOS smart phones via Bluetooth. It supports both live streaming as well as transferring data at the end of a match. It seems to come with a racket charger you can plug your racket into \cite{sotxhw}, but it advertises wireless charging, how those two things work together is not documented.

From the look of the app in the feature picture on an article on LinkedIn \citep{sotxapp}, it seems like it focus mostly on what kind of swing you perform. But can also keep track on how long you have been working out, calories burned and max speed.

\section*{Holy Pie Smart Racket}
In 2014 a Kickstarter campaign called Holy Pie Smart Racket launched \citep{holypie}. It successfully raised \$2010 with four backers. They made a system for both badminton and tennis. It is tough to tell what this product can do since their website is mostly in Chinese and seems unfinished as most of the links do not work and there is still dummy text present \citep{holypi}.

\section*{USENSE}
USENSE is a sensor that you mount at the bottom of the racket shaft \citep{usense}. There is an Android and iOS application so that it can connect to your smart phone through Bluetooth 4.0+ or Bluetooth 2.0. Both specifications are mentioned. This one is significantly different from the other two because you do not need to buy a new badminton racket, you only buy a sensor and mount it. A downside might be that it is not integrated into the racket and changes the balance of the racket.	

\section*{Reflection}
All of these products seem very undocumented and their websites are either unfinished or cumbersome to understand, especially the English language ones. They are only available through smart phone applications and not on desktops which may be use full for coaches.