\chapter{Relevant literature}
The following is a list of potential interesting documents related to technological decisions to be made in the early part of the project.

\subsection*{Articles}

\textbf{Building Cross Platform Applications} \newline
Practices and architectural overview \newline
\url{https://developer.xamarin.com/guides/cross-platform/application_fundamentals/building_cross_platform_applications/}

\textbf{The New Age of Cross-Platform Mobile App Development} \newline
A short article on the pitfalls of cross-platform development. \newline
\url{http://tech.co/cross-platform-mobile-app-development-2-2015-07}

\textbf{New Cross Platform App Development Tools in 2016} \newline
An article listing new tools available in 2016 for cross platform development. \newline
\url{http://goo.gl/HhGqbl}

\textbf{10 cross-platform mobile development tools for enterprises} \newline
Article on the complications with cross-platform development and what possibilities there are for enterprises. \newline
\url{http://techbeacon.com/10-cross-platform-mobile-development-tools-enterprises}

\subsection*{Frameworks}
Here follows some links to documentations and overviews for different framework possibilities.

\textbf{Introduction to Meteor} \newline
Main concept walk through and feature descriptions. \newline
\url{http://guide.meteor.com/index.html}

\textbf{Introduction to Nativescript} \newline
Main concepts and a good FAQ. \newline
\url{https://docs.nativescript.org/start/introduction}

\textbf{Where does the Ionic Framework fit in?} \newline
Overview introduction to the Ionic framework and the possibilities within. \newline
\url{http://blog.ionic.io/where-does-the-ionic-framework-fit-in/}

\textbf{Cross Platform Mobile Development Tools: \newline Ending the iOS vs. Android debate} \newline
Top 10 list of available cross platform framework. Dated 2015, so things have changed since, but some might still be relevant. \newline
\url{http://goo.gl/ZP7QrZ}

\textbf{Haxe introduction} \newline
An OSS platform for \textbf{many} targets with compatibility to iOS, Android, Node.js and many others. \newline
\url{http://haxe.org/}

\textbf{Adobe PhoneGap documentation} \newline
Introduction to the concepts and framework possibilities. \newline
\url{http://docs.phonegap.com/}