\chapter{Requirements}
This chapter lists the initial requirements identified for the project i.e. a tentative list. The following user stories are used to identify the functional requirements.

\userstory{As a consultant, I want to present recorded data on an athletes performance in a nice fashion that makes the athlete understand and become interested in the product.}
\userstory{As a consultant, I want to be able to get recorded data anywhere as long as I am connected to the internet.}
\userstory{As a consultant, I want to organize my recorded performances for users in their corresponding clubs.}

\section*{Functional requirements}
The requirements are split into two sections. One regarding the application the consultant will be using. The other one is the backend requirements to enable the application's goals.

\subsection*{Application}
The application must
\begin{itemize}
	\item Present the available key features of a performance in a clear and understandable way for both the consultant and the athlete.
	\item Enable the consultant to input data from a performance sensor into the application and implicitly push this data to an externalized location.
	\item Let the consultant manage what athlete did the current performance.
	\item Enable the consultant to find athletes' old performances stored on an externalized location.
	\item Enable to consultant to organize athletes in clubs to ease future lookup.
\end{itemize}

\subsection*{Server}
The backend must
\begin{itemize}
	\item Enable clients to post new performance measurements on to the stores.
	\item Enable clients to post metadata on athletes and clubs on to the stores.
	\item Provide key features of performances available to clients.
	\item Be able to calculate key features from the performance sensor.
	\item Calculate features asynchronously and notify clients processing is done and data is available.
\end{itemize}

\section*{Non-functional requirements}
The following non-functional requirements are specified for the project.

\begin{itemize}
	\item The project should mainly use Open Source Software.
	\item The application should run on multiple platforms.
\end{itemize}

The last item may be subject to change if the user analysis proves it to be redundant.
